---
title: "My Fancy Presentation"
author: "John B Cheadle"
date: "February 17, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My New Slide

Some content

*** 
A slide without a title

## Bullets

 - Bullet 1
 - Bullet 2

1. Item a
2. Item b

## My Title

### Top-level Subheading

#### Second-Level Subheading

Plain Text

*italicized text*

**Bold Text**

`for (i %in% 1:10)`


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

